Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-03-25 appendices/chGratingDesign/chapter-gratingdesign.tex
move the protochapters into the appendices directory, since that is their ultimate destination

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=Rnum,height=4.25in,width=5.5in}
\caption[Illustration of Si gratings of different blaze angles]{Illustration of Si gratings of different blaze angles, and the concomitant microscopic Si V-groove cross section.  The grooves are symmetric for R1.4, and increasingly asymmetric for larger blaze angles.  The apex angle of the cross section is 70.5$\deg$ in all cases; it is set by the Si crystal structure and is minutely increased by the finite anisotropic etch ratio.}
\label{fig:Rnum}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=gt_geom_blockage.pdf,height=3in,width=6.4in}
\caption[Schematic of groove top geometry]{Schematic of groove top geometry.  The cartoon gratings have the same blaze angle and period, but different groove top widths (fill factors).  There is a critical groove top width to period ratio below which the groove tops are completely shadowed and no geometric blockage occurs.  For an R3 grating as used in iSHELL, the critical fraction is $t/\sigma < 0.51$.  The delivered devices have $t/\sigma = 0.375$, which is similar to the schematic on the right side.}
\label{fig:groovetop}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=IG_blaze_design,height=6.5in,width=3.25in}
\caption[Grating design considerations that depend on the choice of blaze angle]{Three paneled plot showing three grating design considerations that depend on the choice of blaze angle.  The top pane shows the range of groove top to grating period ratios that result in shadowed groove tops, or efficiency loss from exposed groove tops.  The middle pane shows the angle at which a Si boule must be cut to produce Si V groove facets at the given blaze angle.  The thickness of the line in the middle pane is equal to the range in cutting angle depending on the degree of anisotropic etching into the (111) Si crystal plane (and concomitant widening of the Si V-groove apex angle).  The width corresponds to $<0.8\deg$.  The bottom pane shows the maximum beam size possible on a 30 mm thick, 100 mm diameter Si substrate, as a function of blaze angle.  The solid line is the beam size, the dashed line is the substrate thickness as measured perpendicular to the grating surface.  These figures are all for Si immersion gratings in Littrow autocollimation.}
\label{fig:IGdesignplot}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=scarp_reflect.pdf,height=2.0in,width=6.3in}
\caption[Scarp facet in reflection]{A diagram illustrating the lengths used to define the scarp face geometry when illuminated in back surface reflection.  The scarp face length $s$ is labelled and shown in the vertical short solid yellow line.  The blaze angle is the enclosed angle of line $s$ and $h$.  The hypotenuse of the right triangle is label $h$ in the long dashed red line.  The short blue dashed line is perpendicular to the scarp face and parallel to the incoming beam.  }
\label{fig:scarpface}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingDesign/Rnum,height=4.25in,width=5.5in}
\caption[Illustration of Si gratings of different blaze angles]{Illustration of Si gratings of different blaze angles, and the concomitant microscopic Si V-groove cross section.  The grooves are symmetric for R1.4, and increasingly asymmetric for larger blaze angles.  The apex angle of the cross section is 70.5$\deg$ in all cases; it is set by the Si crystal structure and is minutely increased by the finite anisotropic etch ratio.}
\label{fig:Rnum}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingDesign/gt_geom_blockage.pdf,height=3in,width=6.4in}
\caption[Schematic of groove top geometry]{Schematic of groove top geometry.  The cartoon gratings have the same blaze angle and period, but different groove top widths (fill factors).  There is a critical groove top width to period ratio below which the groove tops are completely shadowed and no geometric blockage occurs.  For an R3 grating as used in iSHELL, the critical fraction is $t/\sigma < 0.51$.  The delivered devices have $t/\sigma = 0.375$, which is similar to the schematic on the right side.}
\label{fig:groovetop}
\end{center}
\end{figure}

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingDesign/IG_blaze_design.pdf,height=6.5in,width=3.25in}
\caption[Grating design considerations that depend on the choice of blaze angle]{Three paneled plot showing three grating design considerations that depend on the choice of blaze angle.  The top pane shows the range of groove top to grating period ratios that result in shadowed groove tops, or efficiency loss from exposed groove tops.  The middle pane shows the angle at which a Si boule must be cut to produce Si V groove facets at the given blaze angle.  The thickness of the line in the middle pane is equal to the range in cutting angle depending on the degree of anisotropic etching into the (111) Si crystal plane (and concomitant widening of the Si V-groove apex angle).  The width corresponds to $<0.8\deg$.  The bottom pane shows the maximum beam size possible on a 30 mm thick, 100 mm diameter Si substrate, as a function of blaze angle.  The solid line is the beam size, the dashed line is the substrate thickness as measured perpendicular to the grating surface.  These figures are all for Si immersion gratings in Littrow autocollimation.}
\label{fig:IGdesignplot}
\end{center}
\end{figure}

@@

\begin{figure}[h!] 
\begin{center}
\ \psfig{file=chGratingDesign/scarp_reflect.pdf,height=2.0in,width=6.3in}
\caption[Scarp facet in reflection]{A diagram illustrating the lengths used to define the scarp face geometry when illuminated in back surface reflection.  The scarp face length $s$ is labelled and shown in the vertical short solid yellow line.  The blaze angle is the enclosed angle of line $s$ and $h$.  The hypotenuse of the right triangle is label $h$ in the long dashed red line.  The short blue dashed line is perpendicular to the scarp face and parallel to the incoming beam.  }
\label{fig:scarpface}
\end{center}
\end{figure}

### 2015-03-25 appendices/chIshell/chapter-ishellgratings.tex
move the protochapters into the appendices directory, since that is their ultimate destination

\begin{figure}[htb] 
\begin{center}
\subfloat[Example M band blaze envelope]{\ \psfig{file=ishell_Mband,height=3.8in,width=5.6in}}
\
\subfloat[Example L band blaze envelope]{\ \psfig{file=ishell_Lband,height=3.8in,width=5.6in}}
\caption[Calculated $L-$ and $M-$ band blaze envelopes for iSHELL]{ L and M band blaze envelopes calculated from scalar diffraction theory in immersion.  The refractive index is based on the (cite XX) Sellmeier equations for Si at room temperature (T$=295$ K).}
\label{fig:LMbandcalc}
\end{center}
\end{figure}

\begin{figure}[htb] 
\begin{center}
\subfloat[Example K band blaze envelope]{\ \psfig{file=ishell_Kband,height=3.8in,width=5.6in}}
\
\subfloat[Example J band blaze envelope]{\ \psfig{file=ishell_Jband,height=3.8in,width=5.6in}}
\caption[Calculated $J-$ and $K-$ band blaze envelopes for iSHELL]{ J and K band blaze envelopes calculated from scalar diffraction theory in immersion.  The refractive index is based on the (cite XX) Sellmeier equations for Si at room temperature (T$=295$ K).}
\label{fig:JKbandcalc}
\end{center}
\end{figure}

>>>>

\begin{figure}[htb] 
\begin{center}
\subfloat[Example M band blaze envelope]{\ \psfig{file=chIshell/ishell_Mband.pdf,height=3.8in,width=5.6in}}
\
\subfloat[Example L band blaze envelope]{\ \psfig{file=chIshell/ishell_Lband.pdf,height=3.8in,width=5.6in}}
\caption[Calculated $L-$ and $M-$ band blaze envelopes for iSHELL]{ L and M band blaze envelopes calculated from scalar diffraction theory in immersion.  The refractive index is based on the (cite XX) Sellmeier equations for Si at room temperature (T$=295$ K).}
\label{fig:LMbandcalc}
\end{center}
\end{figure}

\begin{figure}[htb] 
\begin{center}
\subfloat[Example K band blaze envelope]{\ \psfig{file=chIshell/ishell_Kband.pdf,height=3.8in,width=5.6in}}
\
\subfloat[Example J band blaze envelope]{\ \psfig{file=chIshell/ishell_Jband.pdf,height=3.8in,width=5.6in}}
\caption[Calculated $J-$ and $K-$ band blaze envelopes for iSHELL]{ J and K band blaze envelopes calculated from scalar diffraction theory in immersion.  The refractive index is based on the (cite XX) Sellmeier equations for Si at room temperature (T$=295$ K).}
\label{fig:JKbandcalc}
\end{center}
\end{figure}
